Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-03 ijar-npb-ms.tex
rewritten write-out of monotonicity in y argument

The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
\label{eq:postpredCny}
\end{align}
%\td{leave this equation out???}

@@

***Lower and upper bounds for $\Rsys(t)$ by min and max over $\PtZi{1}, \ldots, \PtZi{K}$.

***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align*}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)}\\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,.
\end{align*}

We need to optimize over $\nktz$'s only,
as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
Remember that $\yktz$ gives the prior expected survival probability for a component of type $k$ at time $t$.
As seen in Figures *** and ***, the posterior parameter set bounds are the transformed prior parameter set bounds,
i.e., $\yktzu$ corresponds to the upper bound of $\PktN$ for all $\nktz \in \PktZ$.

Now, a higher posterior expected survival probability means
higher probability for many components surviving out of $m_k$
(i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower).
***Indeed, the Beta-binomial distribution is stochastically ordered for varying y, i.e.,
its cdf is decreasing in $\yktn$ for fixed $l_k$, and the cdfs for different $\yktn$ do not cross each other.***
This means that for $\yktn$ the probability weights given to the high values of $l_k$ are maximised.
As $\Phi$ is non-decreasing in each of its arguments $l_k, k=1,\ldots,K$ (for coherent systems),
$\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values.

%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.

>>>>

The Beta-binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,,
\label{eq:postpredCny}
\end{align}
and the corresponding cumulative mass function (cmf) is given by
\begin{align}
F_{C^k_t\mid s^k_t}(l_k) &= P(C^k_t \le l_k \mid s^k_t) = \sum_{j_k=0}^{l_k} P(C^k_t = j_k \mid s^k_t)\,.
\label{eq:postpredCnycmf}
\end{align}

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~*** over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.
It turns out that we need to optimise over $\nktz$ ($k=1,\ldots,K$) only,
as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.

To see this,
remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%the posterior parameter set bounds are the transformed prior parameter set bounds,
%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%
Now, a higher posterior expected functioning probability means
higher probability for many components out of $m_k$ surviving,
i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
***Indeed, the Beta-binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
such that the cmfs for different values of $\yktn$ do not cross each other.***
This means that for each fixed $\nktz$, the Beta-binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align*}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)}\\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,.
\end{align*}
